Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-22 paper/main.tex
homset

@@

@@

The model described in this work provides a model for expressing data sets with different topological properties.

\subsection{Fiber Bundles}
We obtain this generality by using a mathematical structure called a fiber bundles as the basis of our abstraction, as proposed by Butler, Bryson, and Pendley\cite{butlerVisualizationModelBased1989,
butlerVectorBundleClassesForm1992}. As described by them, a fiber bundle is a formal model of the mapping between data points and the underlying topological space they lie in. For example, nodes on a network and the graph of the network, an image and the underlying grid at which the image is sampled, or table columns and the table index.

@@

    (\textcolor{functor}{f^*}\sheafc_{\textcolor{target}{Y}})(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f^*}", color=functor] \arrow[uu, "\textcolor{homset}{Hom_{\sheaf_X}}", color=homset] &  & \sheafc_{\textcolor{target}{Y}}(\textcolor{target}{Y}) \arrow[uu, "\textcolor{homset}{Hom_{\sheaf_Y}}"', color=homset] \arrow[lluu, "\textcolor{homset}{Hom_{XY}}"' description, dashed, color=homset]

@@

meaning that transformations of sections of one sheaf to sections of another are equivalent regardless of the space the sheaf is over.

>>>>

\note{Munzer describes continuiity as,  We obtain this generality by using a mathematical structure called a fiber bundles as the basis of our abstraction, as proposed by Butler, Bryson, and Pendley\cite{butlerVisualizationModelBased1989,
butlerVectorBundleClassesForm1992}}

@@

\note{fig and K&S model, vickers}

@@

The model described in this work provides a model for expressing data sets with different topological properties. We obtain this generality by using a mathematical structure called a fiber bundles as the basis of our abstraction, as proposed by Butler, Bryson, and Pendley\cite{butlerVisualizationModelBased1989,
butlerVectorBundleClassesForm1992}. As described by them, a fiber bundle is a formal model of the mapping between data points and the underlying topological space they lie in. For example, nodes on a network and the graph of the network, an image and the underlying grid at which the image is sampled, or table columns and the table index.

@@

    (\textcolor{functor}{f^*}\sheafc_{\textcolor{target}{Y}})(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f^*}", color=functor] \arrow[uu, "\textcolor{homset}{hom_{\sheaf_X}}", color=homset] &  & \sheafc_{\textcolor{target}{Y}}(\textcolor{target}{Y}) \arrow[uu, "\textcolor{homset}{hom_{\sheaf_Y}}"', color=homset] \arrow[lluu, "\textcolor{homset}{hom_{XY}}"' description, dashed, color=homset]

@@

meaning that morphisms between sections over different topological spaces are equivalent when composed with the pullback and pushforward functor.
